---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: ENIfE
#### Pilot: Lester Tong
#### Co-pilot: Tom Hardwicke  
#### Start date: March 24, 2017
#### End date: March 27, 2017

-------

#### Methods summary: 
Participants saw 4 composite face images, 2 (male vs female) averages of 15 faces (from individuals with high vs low reaction time variability on a cognitive control task). In the discrimination task, participants were presented with both high and low SDRT faces (matched on gender), and asked to indicate which of the two faces was more attractive, physically healthy, and sex-typical. In the ratings task, participants used 9-point Likert scales to rate the individual faces on attractiveness, physical health, and sex-typicality.

------

#### Target outcomes: 
> 2.2.1. Attractiveness judgements

> Consistent with our prediction, low SDRT faces were chosen above chance-level (50%; Fig. 2), both for female composites 91.38% [84.09, 98.67] Cohen’s dz = 1.463 and male composites, 63.79% [51.32, 76.27] Cohen’s dz = 0.28. In addition, low SDRT (highest standard deviation of reaction time) faces were rated as more attractive than high SDRT faces, both for female composites 1.67 [1.11, 2.22] Cohen’s dz = 0.78 and male composites 1.04 [0.5, 1.57] Cohen’s dz = 0.5 (Fig. 2).

> 2.2.2. Physical health and sex-typicality judgments

> For judgements of physical health, low SDRT faces were chosen above chance-level, both for female composites 76.29% [69.43, 83.16] Cohen’s dz = 0.99 and male composites, 66.81% [59.44, 74.18] Cohen’s dz = 0.59 (Supplementary Fig. 1A). In addition, low SDRT faces were rated as more physically healthy than high SDRT faces, both for female composites 0.59 [0.27, 0.92] Cohen’s dz = 0.47 and male composites 0.44 [0.18, 0.69] Cohen’s dz = 0.45 (Supplementary Fig. 1C).

> For sex-typicality judgments, low SDRT faces were chosen above chance-level for female composites 84.48% [75.08, 93.88] Cohen’s dz = 0.94, but not male composites 51.72% [38.75, 64.70] Cohen’s dz = 0.03 (Supplementary Fig. 1A). In addition, low SDRT faces were rated as more sex-typical than high SDRT faces for female composites 1.32 [0.73, 1.90] Cohen’s dz = 0.58, but not male composites 0.35 [−0.21, 0.92] Cohen’s dz = 0.16 (Supplementary Fig. 1C).

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

Some useful packages are being loaded below:

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(readxl) # import excel files
library(CODreports) # custom report functions
library(lsr)
sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))} # custom function for standard error
ci95 <- function(x) {sem(x) * 1.96} # custom function for confidence intervals
```

## Step 2: Load data

```{r}
d_choice <- read_excel("data/data.xlsx", sheet = 1, skip=2)
d_rating <- read_excel("data/data.xlsx",sheet=2,skip=3)
```

## Step 3: Tidy data

Rename columns:

```{r}
colnames(d_choice) <- c("participant_ID","gender","Attractiveness_Female","Attractiveness_Male","Health_Female","Health_Male","Typical_Female","Typical_Male")
d_choice <- d_choice %>%
  select(-gender)

colnames(d_rating) <- c("participant_ID","gender","Attractiveness_Female_LowSDRT","Attractiveness_Female_HighSDRT","Attractiveness_Male_LowSDRT","Attractiveness_Male_HighSDRT","Health_Female_LowSDRT","Health_Female_HighSDRT","Health_Male_LowSDRT","Health_Male_HighSDRT","Typical_Female_LowSDRT","Typical_Female_HighSDRT","Typical_Male_LowSDRT","Typical_Male_HighSDRT")
d_rating <- d_rating %>%
  select(-gender)
```

Tidy data:

```{r}
discrimination <- d_choice %>% gather(condition,lowSDRTchoice,Attractiveness_Female:Typical_Male) %>% separate(condition,c("Feature","Gender"),sep="_")

ratings <- d_rating %>% gather(condition,rating,Attractiveness_Female_LowSDRT:Typical_Male_HighSDRT) %>% 
  separate(condition,c("Feature","Gender","SDRT"),sep="_")  %>%
  spread(SDRT,rating) %>%
  mutate(diffscore=LowSDRT-HighSDRT)
```

## Step 4: Run analysis

Calculate summary statistics:

```{r}
## summarize scores to obtain means, standard errors, 95% confidence intervals, and cohen's Dzs
discrimination_sum <- discrimination %>% 
  group_by(Feature,Gender) %>%  
  summarize(mean=mean(lowSDRTchoice),n=length(lowSDRTchoice), std.error = sem(lowSDRTchoice), CI_lb = mean - ci95(lowSDRTchoice), CI_ub = mean + ci95(lowSDRTchoice), dz = cohensD(lowSDRTchoice - 50))

ratings_sum <- ratings %>% 
  group_by(Feature,Gender) %>%  
  summarize(mean=mean(diffscore),sd=sd(diffscore), se = sem(diffscore), CI_lb = mean - ci95(diffscore), CI_ub = mean + ci95(diffscore), dz = cohensD(diffscore))
```

Reproduce target outcome:

> Consistent with our prediction, low SDRT faces were chosen above chance-level (50%; Fig. 2), both for female composites 91.38% [84.09, 98.67] Cohen’s dz = 1.463 and...

```{r 2.2.1.1}
###Female attractiveness
fa <- discrimination_sum %>% filter(Feature == 'Attractiveness', Gender == 'Female')
## Point estimate
compareValues(reportedValue=91.38,obtainedValue=fa$mean)
## 95% CI bounds
compareValues(reportedValue=84.09,obtainedValue=fa$CI_lb)
compareValues(reportedValue=98.67,obtainedValue=fa$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=1.46,obtainedValue=fa$dz)
```

Reproduce target outcome:

> ...male composites, 63.79% [51.32, 76.27] Cohen’s dz = 0.28. 

```{r 2.2.1.2}
### Male attractiveness:
ma <- discrimination_sum %>% filter(Feature == 'Attractiveness', Gender == 'Male')
## Point estimate
compareValues(reportedValue=63.79,obtainedValue=ma$mean)
## 95% CI bounds:
compareValues(reportedValue=51.32,obtainedValue=ma$CI_lb)
compareValues(reportedValue=76.27,obtainedValue=ma$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.28,obtainedValue=ma$dz)
```

Reproduce target outcome:

> In addition, low SDRT (highest standard deviation of reaction time) faces were rated as more attractive than high SDRT faces, both for female composites 1.67 [1.11, 2.22] Cohen’s dz = 0.78 and...

```{r 2.2.1.3}
###Female attractiveness ratings:
fa_rat <- ratings_sum %>% filter(Feature == 'Attractiveness', Gender == 'Female')
## Point estimate
compareValues(reportedValue=1.67,obtainedValue=fa_rat$mean)
## 95% CI bounds:
compareValues(reportedValue=1.11,obtainedValue=fa_rat$CI_lb)
compareValues(reportedValue=2.22,obtainedValue=fa_rat$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.78,obtainedValue=fa_rat$dz)
```

Reproduce target outcome:

> ...male composites 1.04 [0.5, 1.57] Cohen’s dz = 0.5 (Fig. 2).

```{r 2.2.1.4}
###Male attractiveness ratings:
ma_rat <- ratings_sum %>% filter(Feature == 'Attractiveness', Gender == 'Male')
## Point estimate
compareValues(reportedValue=1.04,obtainedValue=ma_rat$mean)
## 95% CI bounds (male):
compareValues(reportedValue=0.50,obtainedValue=ma_rat$CI_lb)
compareValues(reportedValue=1.57,obtainedValue=ma_rat$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.50,obtainedValue=ma_rat$dz)
```

Reproduce target outcome:

> For judgements of physical health, low SDRT faces were chosen above chance-level, both for female composites 76.29% [69.43, 83.16] Cohen’s dz = 0.99 and... 

```{r 2.2.2.1}
###Female health:
fh <- discrimination_sum %>% filter(Feature == 'Health', Gender == 'Female')
## Point estimate
compareValues(reportedValue=76.29,obtainedValue=fh$mean)
## 95% CI bounds
compareValues(reportedValue=69.43,obtainedValue=fh$CI_lb)
compareValues(reportedValue=83.16,obtainedValue=fh$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.99,obtainedValue=fh$dz)
```
Reproduce target outcome:

> ...male composites, 66.81% [59.44, 74.18] Cohen’s dz = 0.59 (Supplementary Fig. 1A). 

```{r 2.2.2.2}
### Male health:
mh <- discrimination_sum %>% filter(Feature == 'Health', Gender == 'Male')
## Point estimate
compareValues(reportedValue=66.81,obtainedValue=mh$mean)
## 95% CI bounds:
compareValues(reportedValue=59.44,obtainedValue=mh$CI_lb)
compareValues(reportedValue=74.18,obtainedValue=mh$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.59,obtainedValue=mh$dz)
```

Reproduce target outcome:

> In addition, low SDRT faces were rated as more physically healthy than high SDRT faces, both for female composites 0.59 [0.27, 0.92] Cohen’s dz = 0.47 and...

```{r 2.2.2.3}
###Female health ratings:
fh_rat <- ratings_sum %>% filter(Feature == 'Health', Gender == 'Female')
## Point estimate
compareValues(reportedValue=0.59,obtainedValue=fh_rat$mean)
## 95% CI bounds:
compareValues(reportedValue=0.27,obtainedValue=fh_rat$CI_lb)
compareValues(reportedValue=0.92,obtainedValue=fh_rat$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.47,obtainedValue=fh_rat$dz)
```

Reproduce target outcome:

> ...male composites 0.44 [0.18, 0.69] Cohen’s dz = 0.45 (Supplementary Fig. 1C).

```{r 2.2.2.4}
###Male health ratings:
mh_rat <- ratings_sum %>% filter(Feature == 'Health', Gender == 'Male')
## Point estimate
compareValues(reportedValue=0.44,obtainedValue=mh_rat$mean)
## 95% CI bounds:
compareValues(reportedValue=0.18,obtainedValue=mh_rat$CI_lb)
compareValues(reportedValue=0.69,obtainedValue=mh_rat$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.45,obtainedValue=mh_rat$dz)
```

Reproduce target outcome:

> For sex-typicality judgments, low SDRT faces were chosen above chance-level for female composites 84.48% [75.08, 93.88] Cohen’s dz = 0.94...

```{r 2.2.2.5}
###Female typicality:
ft <- discrimination_sum %>% filter(Feature == 'Typical', Gender == 'Female')

## Point estimate
compareValues(reportedValue=84.48,obtainedValue=ft$mean)
## 95% CI bounds:
compareValues(reportedValue=75.08,obtainedValue=ft$CI_lb)
compareValues(reportedValue=93.88,obtainedValue=ft$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.94,obtainedValue=ft$dz)
```

Reproduce target outcome:

> ...but not male composites 51.72% [38.75, 64.70] Cohen’s dz = 0.03 (Supplementary Fig. 1A). 

```{r 2.2.2.6}
### Male typicality:
mt <- discrimination_sum %>% filter(Feature == 'Typical', Gender == 'Male')

## Point estimate
compareValues(reportedValue=51.72,obtainedValue=mt$mean)
## 95% CI bounds:
compareValues(reportedValue=38.75,obtainedValue=mt$CI_lb)
compareValues(reportedValue=64.70,obtainedValue=mt$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.03,obtainedValue=mt$dz)
```

Reproduce target outcome:

> In addition, low SDRT faces were rated as more sex-typical than high SDRT faces for female composites 1.32 [0.73, 1.90] Cohen’s dz = 0.58...

```{r 2.2.2.7}
###Female typicality ratings:
ft_rat <- ratings_sum %>% filter(Feature == 'Typical', Gender == 'Female')

## Point estimate
compareValues(reportedValue=1.32,obtainedValue=ft_rat$mean)
## 95% CI bounds:
compareValues(reportedValue=0.73,obtainedValue=ft_rat$CI_lb)
compareValues(reportedValue=1.90,obtainedValue=ft_rat$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.58,obtainedValue=ft_rat$dz)
```

Reproduce target outcome:

> ...but not male composites 0.35 [−0.21, 0.92] Cohen’s dz = 0.16 (Supplementary Fig. 1C).

```{r 2.2.2.8}
###Male typicality ratings:
mt_rat <- ratings_sum %>% filter(Feature == 'Typical', Gender == 'Male')

## Point estimate
compareValues(reportedValue=0.35,obtainedValue=mt_rat$mean)
## 95% CI bounds:
compareValues(reportedValue=-0.21,obtainedValue=mt_rat$CI_lb)
compareValues(reportedValue=0.92,obtainedValue=mt_rat$CI_ub)
## Cohen's Dz:
compareValues(reportedValue=0.16,obtainedValue=mt_rat$dz)

```

## Step 5: Conclusion

```{r}
codReport(Report_Type='joint',
          Article_ID='ENIfE',
          Insufficient_Information_Errors=0,
          Decision_Errors=0,
          Major_Numerical_Errors=0,
          Minor_Numerical_Errors = 0,
          Author_Assistance = F)
```

Overall the reproducibility check was a success. All target outcomes were successfully reproduced.

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
